\newpage
\section{Conclusion}
\begin{itemize}
	\item The importance of this is: the dataset with the longest record reveals the potential variability in two institutions over time; wrt to instruments, users, and associated combustion/graphitization blanks that can all lead to small but persistent offsets that may propagate through the science. This Heidelberg intercomparison shows that in order to get meaningful understandings of the true intercomparability of institutions over time, it must be constantly repeated. 
	\item if the data with the longest available record shows not only changes, but gradients of changes in time with instrument changes, it seeds doubt in the ability to use a short term intercomparison (such as SIO/LLNL) or ANSTO, for long-term offset corrections. 
	\item Where do the offsets come from? Since normalizations to ox-1 should be the same, perhaps they come from combustion and graphitization? Perhaps they come from blank correction strategies? A good way to deal with this/ try to explore this is to have "nested" intercomparisons for example 1) we are all sent graphitze/zinc tubes and press them in house, therefore excluding combustion/graphitization blanks 2) send CO2 in breakseals (what we normally do), and 3) perhaps share blank-correction codes/excel sheets, python codes, software (Fudger, CALAMS), more widely so that users can test differences/intercomparability and edit if they see fit. 
	\item this is something we will address in upcoming iterations of intercomparison, similar to ~\cite{miller2013}. 
    \item these data are hopefully going to be used to offset correct some more data for a new work...can they be trusted? 
    \item how did the NWT3 and NWT4 data compare to the results from Miller 2013? 
    \item Don't forget to mention the Instaar reults/comparison highlighted in Turnbull 2015b.
    \item For SIO/LLNL, the data are within error, but still statistically different. What do we do if, they are the same within error but the difference is still larger than the GGMT threshold? Need to reduce error, which is quite difficult
    
\end{itemize}
    